### 2017-04-16 paper/oopsla17-submission/evaluation.tex
asd

\section{Quantitative Evaluation}
\label{sec:evaluation}
\input{data}

We have implemented our technique for localizing type errors for a
purely functional subset of \ocaml with polymorphic types and functions.
%
We seek to answer three questions in our evaluation:
%
\begin{description}
\item[1. Blame Accuracy (\autoref{sec:quantitative})]
  %
  How often do we \emph{correctly} assign blame for the type error?
  %
  % We compare our technique with a variety of off-the-shelf classifiers
  % and find that our top-ranked blame assignments have an accuracy of
  % 72\%, compared to a state-of-the-art 56\%.
  % For how many ill-typed programs can we accurately predict the source
  % of the error?
\item[2. Feature Utility (\autoref{sec:feature-utility})]
  %
  Which feature sets are \emph{most important} for accurate predictions?
  % How much do the features described in \autoref{sec:features}
  % contribute to our predictions?
\item[3. Explaining Predictions (\autoref{sec:qualitative})]
  %
  Can we \emph{explain} individual predictions (correct or not)?
\end{description}
%\ES{may want to swap (1) and (2)..}

>>>>

\mysection{Quantitative Evaluation}
\label{sec:evaluation}
\input{data}

We have implemented our technique for localizing type errors for a
purely functional subset of \ocaml with polymorphic types and functions.
%
We seek to answer three questions in our evaluation:
%
\begin{itemize}
\item \textbf{How accurate is \toolname?}
  %
  How often does \toolname
  blame a \emph{correct}
  location
  for the type error?
  (\autoref{sec:quantitative})
  %
  % We compare our technique with a variety of off-the-shelf classifiers
  % and find that our top-ranked blame assignments have an accuracy of
  % 72\%, compared to a state-of-the-art 56\%.
  % For how many ill-typed programs can we accurately predict the source
  % of the error?
\item \textbf{What features are used by \toolname?}
  %
  Which program features are the most
  \emph{most important} for
  localizing errors?
   (\autoref{sec:feature-utility})
  % How much do the features described in \autoref{sec:features}
  % contribute to our predictions?
\item[Why does \toolname work? (\autoref{sec:qualitative})]
  %
  Do the models learned by \toolname
  correspond to our intuition about
  the real causes of errors? That is,
  can we \emph{interpret} the individual
  predictions (correct or not)?
\end{itemize}
%\ES{may want to swap (1) and (2)..}

1. MLP-500 (fancy) is 72% vs Sherrloc 56% for top-1
2. Logistic (simple) is 60% vs Sherrloc 56% for top-1
3. MLP-500 reaches 91% for top-3
4. InSlice is crucial, just InSlice + LocalSyntax gets Logistic 10pts higher than OCaml, on par with Sherrloc
5. Typing features provide more bang/buck than contextual syntax
6. Tree learns some simple and intuitive rules for predicting no-blame (e.g. defining a function is a fine thing to do, calling a function likewise)
7.

### 2017-04-16 paper/oopsla17-submission/related.tex
asd

\mysection{Related Work}
\label{sec:related-work}

In this section we describe two relevant aspects of related work:
%
programming languages approaches to diagnosing type errors, and
%
software engineering approaches to fault localization.
%
% applying machine learning techniques to problems in programming languages.

\mysubsection{Type Error Diagnosis}
\label{sec:type-error-diagnosis}
Languages with static type systems and type inference produce type
errors that novices often perceive as difficult to
interpret~\citep{Wand1986-nw}.
%
For example, approaches based on Hindley-Milner or other constraint
systems typically have the issue that when the constraint $\alpha=\beta$
is violated, the system cannot know whether the user should intend to
fix $\alpha$ or $\beta$ and must thus report the discrepancy in a
generic manner.
%
As a result, a number of approaches have been proposed to
more precisely localize the type error,
give clearer error messages, or
fix the error automatically.
%
% The technique most related to our work is \ES{TODO}.  It has been shown
% to be quite good at \ES{TODO}. However, we choose to focus on \ES{TODO},
% and our approach contains \ES{TODO}, which is not present in previous
% work.

@@

\mysubsection{Fault Localization}
Given a defect, \emph{fault localization} is the task of identifying
``suspicious'' program elements (\eg lines, statements) that are likely
implicated in the defect %(\ie that should be changed to fix the defect)
%
--- thus, type error localization can be viewed as an instance of fault
localization.
%
The best-known fault localization technique is likely Tarantula, which
uses a simple mathematical formula based on measured information from
dynamic normal and buggy runs~\citep{Jones2002-us}.
%
Other similar approaches, including those of \citet{Chen2002-qz} and
\citet{Abreu2006-fn,Abreu2007-mu} consider alternate features of
information or refined formulae and generally obtain more precise
results; see \citet{Wong2009-pd} for a survey.
%
While some researchers have approached such fault localization with an
eye toward optimality (\eg \citet{Yoo2013-rw} determine optimal
coefficients), in general such fault localization approaches are limited
by their reliance on either running tests or including relevant
features.
%
For example, Tarantula-based techniques require a normal and a buggy run
of the program.
%
By contrast, we consider incomplete programs with type errors that may
not be executed in any standard sense.
%
Similarly, the features available influence the classes of defects that
can be localized.
%
For example, a fault localization scheme based purely on control flow features
will have difficulty with cross-site scripting or SQL code injection
attacks, which follow the same control flow path on normal and buggy
runs (differing only in the user-supplied data).
%
Our feature set is comprised entirely of syntactic and typing features,
a natural choice for modeling type errors, but it would likely not
generalize to other types of defects.

>>>>

\mysection{Related Work}
\label{sec:related-work}
\label{sec:type-error-diagnosis}

In this section we describe two relevant aspects of related work:
%
programming languages approaches to diagnosing type errors, and
%
software engineering approaches to fault localization.
%
% applying machine learning techniques to problems in programming languages.
%
% \mysubsection{Type Error Diagnosis}
Languages with static type systems and type inference produce type
errors that novices often perceive as difficult to
interpret~\citep{Wand1986-nw}.
%
For example, approaches based on Hindley-Milner or other constraint
systems typically have the issue that when the constraint $\alpha=\beta$
is violated, the system cannot know whether the user should intend to
fix $\alpha$ or $\beta$ and must thus report the discrepancy in a
generic manner.
%
As a result, a number of approaches have been proposed to
more precisely localize the type error,
give clearer error messages, or
fix the error automatically.
%
% The technique most related to our work is \ES{TODO}.  It has been shown
% to be quite good at \ES{TODO}. However, we choose to focus on \ES{TODO},
% and our approach contains \ES{TODO}, which is not present in previous
% work.

@@

\mypara{Fault Localization}
%
Given a defect, \emph{fault localization} is the task of identifying
``suspicious'' program elements (\eg lines, statements) that are likely
implicated in the defect %(\ie that should be changed to fix the defect)
%
--- thus, type error localization can be viewed as an instance of fault
localization.
%
The best-known fault localization technique is likely Tarantula, which
uses a simple mathematical formula based on measured information from
dynamic normal and buggy runs~\citep{Jones2002-us}.
%
Other similar approaches, including those of \citet{Chen2002-qz} and
\citet{Abreu2006-fn,Abreu2007-mu} consider alternate features of
information or refined formulae and generally obtain more precise
results; see \citet{Wong2009-pd} for a survey.
%
While some researchers have approached such fault localization with an
eye toward optimality (\eg \citet{Yoo2013-rw} determine optimal
coefficients), in general such fault localization approaches are limited
by their reliance on either running tests or including relevant
features.
%
For example, Tarantula-based techniques require a normal and a buggy run
of the program.
%
By contrast, we consider incomplete programs with type errors that may
not be executed in any standard sense.
%
Similarly, the features available influence the classes of defects that
can be localized.
%
For example, a fault localization scheme based purely on control flow features
will have difficulty with cross-site scripting or SQL code injection
attacks, which follow the same control flow path on normal and buggy
runs (differing only in the user-supplied data).
%
Our feature set is comprised entirely of syntactic and typing features,
a natural choice for modeling type errors, but it would likely not
generalize to other types of defects.
